%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Khaja Masroor Ahmed}
\address{Norfolk, VA - 23505}
\contacts{(757) 971-7823}
\github{https://www.github.com/khajamasroorahmed}
\linkedin{https://www.linkedin.com/in/khajamasroorahmed}
\email{khajamasroorahmed@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Experienced Android Developer}{Dominion Enterprises}{June 2016 -- Current}
			Native Flagship Application
			\begin{itemize}
				\item Architect, build and develop the new native Android and iOS application for homes.com.
				\item Building a clean, stateful, functionally reactive application using RxJava, Dagger 2, MVVM/MVI pattern, etc.
				\item Conduct platform agnostic trainings/knowledge transfer sessions to inspire the team to adopt industry best practices and elevate the team skills.
				\item A strong advocate of writing abstract, functional, reactive, modular and unit testable code.
			\end{itemize}

			Hybrid Development
			\begin{itemize}
				\item Maintain the homes.com flagship hybrid application for iOS and Android while the native application is under development.
				\item Actively re-architecting and supporting the development of the RE/MAX mobile application.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Backend Developer}{Dominion Enterprises}{July 2017 -- November 2017}	
			\begin{itemize}
				\item Co-designed a highly scalable data model for a user account management system for homes.com colloquially named as "MyHomes".
				\item End to end development including by not limited to writing technical specifications, developing code, writing unit tests.
				\item Integrated instant messaging, push notifications and activity feed to support networking capability between users and realtor agents.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Graduate Research Assistant}{Old Dominion University}{Fall 2014 -- Spring 2016}
			Smart City: Traffic Information Aggregator
			\begin{itemize}
				\item Built a prototype application using Raspberry Pi and bluetooth sensors to aggregate the vehicular traffic information at intersections.
				\item This application was part of a larger goal of building a network array of these sensors to help regulate the traffic.
			\end{itemize}
			Indoor Localization System
			\begin{itemize}
				\item Developed an algorithm for calculating the stride length by fusing the mobile device sensors data.
				\item Algorithm was implemented on both iOS and Android to be used for an indoor localization system prototype for a local hospital.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Honeywell Aerospace}{January 2011 -- July 2014}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Norfolk, VA}{Old Dominion University}{Fall 2014 -- May 2016}
			\begin{itemize}
				\item M.S. in Computer Science, May 2005. GPA: 3.3
				\item Coursework: Computer Architecture; Algorithms; Wireless Networking; Design of Network Protocols.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Hyderabad, India}{Vaughn College of Aeronautics}{Fall 2007 -- August 2011}
			\begin{itemize}
				\item B.S. in Electronics Engineering Technology(Avionics). GPA: 3.3
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Kotlin; Java; Javascript; Swift; Python; Scala; Haskell; C++; C; C\#.NET;
				\item MongoDB; SQL; SqLite; MySql;
                \item Android Studio; XCode; Visual Studio;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}